\section{Experiment Skeleton}

\subsection{Purpose}

The experiments in this project are verification experiments rather than
systems-performance experiments. Their role is to validate the specification,
surface counterexamples early, and document the cost and scope of the bounded
checks used during development.

\subsection{Experiment 1: Small-Instance Model Checking}

The current bounded experiment is a smoke test over a tiny finite instance. It
does not yet sweep bounded price and quantity domains; instead, it fixes a
small trader universe and a small order-ID universe and checks the resulting
finite model.

\begin{itemize}[leftmargin=1.5em]
\item \textbf{Inputs:} \texttt{trader := Fin 2}, \texttt{orderId := Fin 3},
with constant initial balances supplied to the theory functions.
\item \textbf{Checks:} whether the finite instance exhibits any violation of
the declared safety and invariant set.
\item \textbf{Outputs to report:} the exact finite bound, whether a
counterexample was found, and the number of explored states.
\end{itemize}

\subsection{Experiment 2: Invariant Checking}

This experiment focuses on proving the main safety properties with Veil's
invariant tooling.

\begin{itemize}[leftmargin=1.5em]
\item \textbf{Goal:} determine whether the chosen invariants are strong enough
to make the main properties inductive.
\item \textbf{Measurements:} which invariants are required, whether
counterexamples to induction appear, and how many preservation checks are
generated across initialization and actions.
\item \textbf{Success criterion:} the declared safety and invariant set passes
deductive checking for the current minimal model.
\end{itemize}

\subsection{Experiment 3: Optional Executable Cross-Check}

If a Velvet matching loop is implemented, compare its outputs on bounded event
streams against the abstract Veil postcondition.

\begin{itemize}[leftmargin=1.5em]
\item \textbf{Goal:} show that the executable loop agrees with the abstract
matching relation on representative small traces.
\item \textbf{Outputs to report:} supported trace sizes, observed mismatches if
any, and the final postcondition used to link code back to the model.
\end{itemize}

\subsection{Reporting Template}

\begin{center}
\begin{tabular}{@{}>{\raggedright}p{3.6cm} p{4.2cm} p{3.0cm} p{4.0cm}@{}}
\textbf{Experiment} & \textbf{Purpose} & \textbf{Variables} & \textbf{What to report} \\
\hline
Bounded model checking & Smoke-test the finite model & Trader bound, order-ID bound, initial theory values & Exact bound, explored states, counterexample found or absent \\
Invariant checking & Prove the declared safety set & Safety count, invariant count, action blocks & Total checks and whether any block fails \\
Optional executable check & Align code with spec & Trace length, supported transition subset & Agreement or mismatch between loop and spec \\
\end{tabular}
\end{center}
