\section{Formal Specification}

\subsection{Book Ordering}

The abstract model uses first-order predicates rather than an explicit sorted
list representation. The buy side is ranked by descending price, with earlier
timestamps breaking ties; the sell side is ranked by ascending price, again
with earlier timestamps breaking ties. These ranking relations induce the
local notion of price-time priority used throughout the proof.

\subsection{Execution Rule}

Submission takes an explicit trader, order identifier, limit price, and
quantity, and activates a fresh order on the corresponding side of the book.
The matching step then considers one best live bid and one best live ask. If
the two orders are compatible, the system produces a trade record, updates
account balances, and removes the matched orders. In the current minimal
model, only full fills are supported, so matching requires equal quantities.

In the specification, \texttt{freshOrder} is a ghost predicate asserting that
the order identifier is absent from both books and from all trade records.
Best-bid is a ghost relation defined directly in Veil syntax (the listings
below transcribe the source with \texttt{/\textbackslash}, \texttt{forall},
and \texttt{!=} standing for the actual \(\wedge\), \(\forall\), and
\(\neq\) glyphs in the \texttt{.lean} file):

\medskip
\begin{quote}
\begin{verbatim}
ghost relation isBestBid (b : orderId) :=
  inBid b /\ forall o, (inBid o /\ o != b) -> betterBid b o
\end{verbatim}
\end{quote}
\medskip

A submission action reads as a short list of preconditions followed by field
assignments and a timestamp bump:

\medskip
\begin{quote}
\begin{verbatim}
action submit_buy (who : trader) (oid : orderId) (px qty : Nat) {
  require freshOrder oid;  require px > 0;  require qty > 0
  inBid oid := true;  bidWho oid := who;  bidPx oid := px
  bidQty oid := qty;  bidTs oid := next_ts;  next_ts := next_ts + 1
}
\end{verbatim}
\end{quote}
\medskip

The matching action is structurally similar: it requires \texttt{isBestBid b},
\texttt{isBestAsk a}, price crossing, equal quantities, distinct traders, and
sufficient buyer cash and seller assets, then performs the asset and cash
transfer and appends the trade record.

\subsection{Trade Log and Account State}

The trade log is part of the formal state rather than an external trace. This
makes trade-field provenance properties straightforward to state and prove: the
recorded price and quantity can be tied directly to the matched ask and bid.
Account balances are also explicit in the state. The verified conservation
result is a frame-style property for uninvolved traders rather than a global
sum theorem, because the latter cannot be expressed in the first-order fragment
that Veil targets.
