\section{Introduction}

Electronic exchanges continuously receive buy and sell orders and maintain an
order book that determines which trades may execute. In the standard
price-time-priority model, higher bids outrank lower bids, lower asks outrank
higher asks, and orders at the same price are filled in arrival order. These
rules are simple to state informally, but implementing and validating them
precisely is non-trivial once one accounts for ordered books, trade logging,
and per-account state updates.

This paper treats a deliberately simplified matching engine as a formal
verification problem. The objective is not to model a production venue with
full market microstructure, but to isolate the exchange core and prove that it
preserves a set of safety properties. Concretely, the target is a
single-asset, limit-order-only engine whose transition relation only permits
legal submission and matching steps, and whose safety properties constrain the
fields and balance effects of recorded trades.

The main contribution is a proof-oriented specification of the matching engine
in Veil, together with a complete deductive verification of seven safety
properties and thirteen supporting invariants. Matching is specified through
first-order best-bid and best-ask predicates rather than by proving a concrete
executable book algorithm correct. This gives a meaningful verified core that
captures the essential correctness requirements of price-time-priority
matching, even though it does not extend to a verified executable
implementation.

\subsection*{Worked Example}

A concrete trace makes the model easier to read. Suppose traders \(T_1\) and
\(T_2\) both start with cash \(=\) asset \(= 100\).

\begin{enumerate}[leftmargin=2em,itemsep=2pt,topsep=2pt]
  \item \texttt{submit\_buy(T1, oid=1, px=10, qty=5)} adds order 1 to the bid
        book at price 10, quantity 5, timestamp 0.
  \item \texttt{submit\_sell(T2, oid=2, px=8, qty=5)} adds order 2 to the ask
        book at price 8, quantity 5, timestamp 1.
  \item \texttt{doMatch(1, 2)} fires: prices cross (\(10 \ge 8\)), quantities
        match, traders differ, balances are sufficient. The engine removes both
        orders, transfers \(8 \times 5 = 40\) cash from \(T_1\) to \(T_2\) and
        5 asset units from \(T_2\) to \(T_1\), and appends
        \texttt{tradeExists(1,2)} with \texttt{tradePx=8}, \texttt{tradeQty=5}.
\end{enumerate}

The verified safety properties pin down exactly this behaviour: the recorded
quantity equals the bid quantity, the recorded price equals the ask price,
buyer and seller differ, and any trader not appearing in a trade keeps their
initial balance.
