\section{Limitations and Future Work}

The model intentionally abstracts away many features of real exchanges:
multiple assets, market orders, cancellation, partial fills, protocol-level
sequencing, and operational resilience. The aim is a clean verified core rather
than a replica of a production trading venue.

Because the specification uses a relational encoding, matching correctness is
expressed through best-order predicates in the transition preconditions rather
than by verifying a concrete book-processing procedure. Extending the work to
a verified executable matching loop---for instance via Velvet---would
strengthen the result by connecting the abstract specification to a runnable
algorithm.

The accounting result is weaker than full global conservation. The proved
invariant is a frame-style property for traders uninvolved in all recorded
trades, not a sum-preservation theorem over all accounts. Expressing the
latter requires quantifying over a summation that falls outside the
first-order fragment supported by Veil's SMT backend.

Finally, bounded model checking is currently disabled. Veil's
\texttt{\#model\_check} command requires a finite \texttt{Enumeration} of each
action's argument tuple, and both submission actions take \texttt{Nat}-typed
price and quantity arguments. To let \texttt{\#gen\_spec} continue to derive
\texttt{Enumeration} for the action-label sum, the specification declares a
stub \texttt{Enumeration Nat} instance whose completeness proof is
\texttt{sorry}. The stub is never evaluated: \texttt{\#model\_check} is
commented out and \texttt{\#check\_invariants} does not depend on it.
Restricting price and quantity to a bounded type such as \texttt{Fin~N} would
re-enable the bounded checker but would also narrow the abstract model.
Replacing the stub with a real \texttt{Enumeration} for a chosen finite price
and quantity range, while leaving the abstract specification otherwise
intact, is a natural follow-up.
