\section{Safety Properties}

The specification declares seven safety properties, organised into three
groups.

The first group concerns well-formedness of active orders: every order in the
bid or ask book must carry a positive quantity. These properties are preserved
trivially by the submission preconditions, and they propagate through matching
because \texttt{doMatch} removes the matched orders entirely rather than
leaving residual quantities.

The second group concerns trade-field provenance. Every recorded trade must
have a positive price and a positive quantity. Beyond positivity, the recorded
quantity must equal the bid quantity of the buy-side order, and the recorded
price must equal the ask price of the sell-side order. A separate property
asserts that the buyer and seller of every recorded trade are distinct traders.

The third group is an accounting property. Traders who are not involved in any
trade---either as buyer or as seller---retain their initial cash and asset
balances. This is a frame-style conservation statement rather than a global
sum-preservation theorem over all accounts, because the latter requires
quantifying over a summation that cannot be expressed in the first-order
fragment supported by Veil's SMT backend.

All seven properties are stated as \texttt{safety} declarations in the Veil
source. Thirteen additional \texttt{invariant} declarations serve as
supporting lemmas that make the safety properties inductive: book disjointness,
timestamp monotonicity and uniqueness, trade-exclusion from both books,
positive prices on active orders, and the balance frame conditions.
